
Loading of libraries
```{r}
library(quantmod)
library(purrr)
library(xts)
library(quadprog)
library(ggplot2)
library(psych)
library(dplyr)
```

Data Collection
```{r}
#Collecting data
symbols = c('QQQ','FEZ','AIA','VNQ','IQQP.DE','UUP','FXE','FXY','FXNAX','SEGA.MI')
prices = 
  getSymbols(symbols, src = 'yahoo', 
             from = "2011-06-01", 
             to = "2021-05-31",
             auto.assign = TRUE, 
             warnings = FALSE) %>% 
  map(~Ad(get(.))) %>% 
  reduce(merge) %>%
  'colnames<-' (symbols)
prices= na.omit(prices)
Date = as.Date(index(prices),format='%Y-%m-%d')
prices.df <- cbind.data.frame(Date,prices[,1:10])
write.csv(prices.df,file='Prices.csv',col.names = T, row.names = F)
```

Loading of CSV data
```{r}
prices = read.csv('Prices.csv')
Date = as.Date(prices$Date,format='%Y-%m-%d')
prices.df = cbind.data.frame(Date, prices[,-1])
prices.xts = xts(prices[,-1],order.by=Date)
ret.xts = diff(log(prices.xts))
ret.xts = na.omit(ret.xts) 
R = ret.xts*100 

prices.1 <- read.csv('Prices_NEW.csv')
Date = as.Date(prices.1$Date,format='%m/%d/%Y')
prices.df.1 = cbind.data.frame(Date, prices.1[,-1])
prices.xts.1 = xts(prices.df.1[,-1],order.by=Date)
ret.1 = diff(log(prices.xts.1))
ret.1 = na.omit(ret.1) #2241 observations
R.new = ret.1*100
```


Portfolio 1 optimisation
```{r}
options(digits=5)
mean = apply(R,2,mean) #10x1 vector
cov = cov(R)  #10x10 variance-covariance matrix
amat.constraint1 = rep(1,10)  
amat.constraint2 = mean
amat.constraint3 = diag(1,nrow=10)
amat = cbind(amat.constraint1,amat.constraint2,amat.constraint3)
bvec.constraint1 = 1
#bvec.constraint2 = muP[i]
bvec.constraint3 = c(0,0,0,0,0,0,0,0,0,0)
wts = matrix(0,nrow=500,ncol=10)
muP = seq(min(mean)+0.0001,max(mean)-0.0001,length=500)
sdP = muP #initialise sdP 

for (i in 1:length(muP)){
  bvec=c(1,muP[i],bvec.constraint3)
  result = solve.QP(Dmat=2*cov, dvec=rep(0,10), Amat=amat,
                    bvec = bvec, meq=2)
  sdP[i] = sqrt(result$value)
  wts[i,] = result$solution
}
wts <- round(wts, 8)
colnames(wts) = c('QQQ','FEZ','AIA','VNQ','IQQP.DE','UUP','FXE','FXY','FXNAX','SEGA.MI')
```

MVF for portfolio 1
```{r}
par(mfrow =c(1,1))
range(sdP) #0.06, 1.32
range(muP) #-0.02, 0.08
plot(sdP,muP,type='l',xlim=c(0,1.4), ylim=c(-0.02,0.2), lty=3, main = 'Plot of MVF of Portfolio 1')
points(sdP[ind],muP[ind],cex=1.5,pch='+')
ind = (sdP==min(sdP))
c(sdP[ind],muP[ind]) #min port sd = 0.062, min port return = 0.0004
c(sdP[muP==max(muP)],muP[muP==max(muP)]) #1.316867 max portfolio return =0.083633
```

Global minimum point (sd,mu) = (0.062,0.0004)

MVF for only equities and bonds
```{r}
R.1 = R[,c(1,2,3,9,10)]
mean.1 = apply(R.1,2,mean) 
cov.1 = cov(R.1)
amat.1 = cbind(rep(1,5),mean.1,diag(1,nrow=5))
wts.1 = matrix(0,nrow=500,ncol=5)
muP.1 = seq(min(mean.1)+0.0001,max(mean.1)-0.0001,length=500)
sdP.1 = muP.1

for (i in 1:length(muP.1)){
  bvec=c(1,muP.1[i],rep(0,5))
  result = solve.QP(Dmat=2*cov.1, dvec=rep(0,5), Amat=amat.1,
                    bvec = bvec, meq=2)
  sdP.1[i] = sqrt(result$value)
  wts.1[i,] = result$solution
}
wts.1 <- round(wts.1, 8)
colnames(wts.1) = c('QQQ','FEZ','AIA','FXNAX','SEGA.MI')

par(mfrow =c(1,1))
range(sdP.1) #0.2, 1.32
range(muP.1) #0.02, 0.08
ind.1 = (sdP.1==min(sdP.1))
plot(sdP,muP,type='l',xlim=c(0,1.4), ylim=c(-0.02,0.2), lty=3, main = 'MVF Comparison')
points(sdP[ind],muP[ind],cex=1.5,pch='+')
lines(sdP.1,muP.1,type='l', lty=3, col='red')
points(sdP.1[ind.1],muP.1[ind.1],cex=1.5,pch='x')
c(sdP.1[ind.1],muP.1[ind.1]) 
c(sdP.1[muP.1==max(muP.1)],muP.1[muP.1==max(muP.1)]) #1.316867 max portfolio return =0.084

```
Global minimum point (sd,mu) for equities and bonds only portfolio = (0.2,0.015)


MVF for only equitieS, bonds and currencies
```{r}
R.2 = R[,c(1,2,3,6,7,8,9,10)]
mean.2 = apply(R.2,2,mean) 
cov.2 = cov(R.2)
amat.2 = cbind(rep(1,8),mean.2,diag(1,nrow=8))
wts.2 = matrix(0,nrow=500,ncol=8)
muP.2 = seq(min(mean.2)+0.0001,max(mean.2)-0.0001,length=500)
sdP.2 = muP.2

for (i in 1:length(muP.2)){
  bvec=c(1,muP.2[i],rep(0,8))
  result = solve.QP(Dmat=2*cov.2, dvec=rep(0,8), Amat=amat.2,
                    bvec = bvec, meq=2)
  sdP.2[i] = sqrt(result$value)
  wts.2[i,] = result$solution
}
wts.2 <- round(wts.2, 8)
colnames(wts.2) = c('QQQ','FEZ','AIA','UUP','FXE','FXY','FXNAX','SEGA.MI')

par(mfrow =c(1,1))
range(sdP.2) #0.2, 1.32
range(muP.2) #0.02, 0.08
ind.2 = (sdP.2==min(sdP.2))
plot(sdP,muP,type='l',xlim=c(0,1.4), ylim=c(-0.02,0.2), lty=3, main = 'MVF Comparison')
points(sdP[ind],muP[ind],cex=1.5,pch='+')
lines(sdP.1,muP.1,type='l', lty=3, col='red')
points(sdP.1[ind.1],muP.1[ind.1],cex=1.5,pch='+')
points(sdP.2[ind.2],muP.2[ind.2],cex=1.5,pch='x')
c(sdP.2[ind.2],muP.2[ind.2]) 

```
Global minimum point (sd,mu) for equities and bonds only portfolio = (0.0629,0.0006184)

plot of weights changes
```{r}
par(mfrow =c(3,2))
plot(muP,wts[,1],type='l',lty=3, main='QQQ')
plot(muP,wts[,2],type='l',lty=3, main='FEZ')
plot(muP,wts[,3],type='l',lty=3, main='AIA')
plot(muP,wts[,4],type='l',lty=3, main='VNQ')
plot(muP,wts[,5],type='l',lty=3, main='IQQP.DE')
plot(muP,wts[,6],type='l',lty=3, main='UUP')
par(mfrow=c(2,2))
plot(muP,wts[,7],type='l',lty=3, main='FXE')
plot(muP,wts[,8],type='l',lty=3, main='FXY')
plot(muP,wts[,9],type='l',lty=3, main='FXNAX')
plot(muP,wts[,10],type='l',lty=3, main='SEGA.MI')

```


Asset Sharpe Ratio Calculation
```{r}
Sharpe = rep(0,10)
for (i in 1:10){
  Sharpe[i] = mean[i]/sqrt(diag(cov)[i]) 
}
cbind.data.frame(Sharpe,sqrt(diag(cov)),mean)
corPlot(cov)
```

Portfolio 2 Optimisation
```{r}
mean.new = apply(R.new,2,mean)
cov.new = cov(R.new)
amat.new = cbind(rep(1,6),mean.new,diag(1,nrow=6))
wts.new = matrix(0,nrow=500,ncol=6)
muP.new = seq(min(mean.new)+0.0001,max(mean.new)-0.0001,length=500)
sdP.new = muP.new  

for (i in 1:length(muP.new)){
  bvec=c(1,muP.new[i],rep(0,6))
  result = solve.QP(Dmat=2*cov.new, dvec=rep(0,6), Amat=amat.new,
                    bvec = bvec, meq=2)
  sdP.new[i] = sqrt(result$value)
  wts.new[i,] = result$solution
}
wts.new <- round(wts.new, 6)
#colnames(wts.new) = c('QQQ','VGK','MCHI','UUP','FXE','FXY','FXNAX','SEGA.MI')
colnames(wts.new) = c('QQQ','UUP','FXE','FXY','FXNAX','SEGA.MI')

par(mfrow =c(1,1))
range(sdP.new) #0.15, 1.10
range(muP.new) #0, 0.055
ind.new = (sdP.new==min(sdP.new))
plot(sdP,muP,type='l',xlim=c(0,1.4), ylim=c(-0.02,0.2), lty=3, main = 'MVF Comparison')
points(sdP[ind],muP[ind],cex=1.5,pch='+')
lines(sdP.new,muP.new,type='l', lty=3, col='red')
points(sdP.new[ind.new],muP.new[ind.new],cex=1.5,pch='x')
```

```{r}
par(mfrow =c(3,2))
plot(muP,wts.new[,1],type='l',lty=3, ylim=c(0,0.5), main='QQQ')
plot(muP,wts.new[,2],type='l',lty=3, ylim=c(0,0.5), main='UUP')
plot(muP,wts.new[,3],type='l',lty=3, ylim=c(0,0.5), main='FXE')
plot(muP,wts.new[,4],type='l',lty=3, ylim=c(0,0.5), main='FXNAX')
plot(muP,wts.new[,5],type='l',lty=3, ylim=c(0,0.5), main='FXY')
plot(muP,wts.new[,6],type='l',lty=3, ylim=c(0,0.5), main='SEGA.MI')


```

Asset Sharpe Ratio Calculation
```{r}
Sharpe.new = rep(0,6)
for (i in 1:6){
  Sharpe.new[i] = mean.new[i]/sqrt(diag(cov.new)[i]) 
}
cbind.data.frame(Sharpe.new,sqrt(diag(cov.new)),mean.new)
corPlot(cov.new)
```


Implementing Holding Constraints: Limiting equities to 0.1
```{r}
mean.test = apply(R.new,2,mean)
cov.test = cov(R.new)
amat.test_3 = diag(1,nrow=6)
amat.test_3[1,1] = -1
amat.test = cbind(rep(1,6),mean.test,amat.test_3)
wts.test = matrix(0,nrow=500,ncol=6)
muP.test = seq(0,0.02,length=500)
sdP.test = muP.test  

for (i in 1:length(muP.test)){
  bvec=c(1,muP.test[i],c(-0.1,0,0,0,0,0))
  result = solve.QP(Dmat=2*cov.test, dvec=rep(0,6), Amat=amat.test,
                    bvec = bvec, meq=2)
  sdP.test[i] = sqrt(result$value)
  wts.test[i,] = result$solution
}
wts.test <- round(wts.test, 6)
colnames(wts.test) = c('QQQ','UUP','FXE','FXY','FXNAX','SEGA.MI')
ind.test = (sdP.test==min(sdP.test))
```


Create unconstraint portfolio for comparison for same range of muP
```{r}
wts.new = matrix(0,nrow=500,ncol=6)
muP.new = seq(0,0.02,length=500)
sdP.new = muP.new 
mean.new = apply(R.new,2,mean)
cov.new = cov(R.new)
amat.new = cbind(rep(1,6),mean.new,diag(1,nrow=6))

for (i in 1:length(muP.new)){
  bvec=c(1,muP.new[i],rep(0,6))
  result = solve.QP(Dmat=2*cov.new, dvec=rep(0,6), Amat=amat.new,
                    bvec = bvec, meq=2)
  sdP.new[i] = sqrt(result$value)
  wts.new[i,] = result$solution
}
wts.new <- round(wts.new, 6)
colnames(wts.new) = c('QQQ','UUP','FXE','FXY','FXNAX','SEGA.MI')
ind.new = (sdP.new==min(sdP.new))


```

```{r}
plot(sdP.new,muP.new,type='l',xlim=c(0,0.6), ylim=c(-0.02,0.02), lty=3, main = 'MVF Comparison: 10% equity holding constraint vs no constraint')
points(sdP.new[ind.new],muP.new[ind.new],cex=1.5,pch='+')
lines(sdP.test,muP.test,type='l', lty=3, col='red')
points(sdP.test[ind.test],muP.test[ind.test],cex=1.5,pch='x')
```

```{r}
par(mfrow =c(3,2))
plot(muP.new,wts.new[,1],type='l',lty=3, xlim=c(0,0.02), main='QQQ')
lines(muP.test,wts.test[,1],type='l',col='red')
plot(muP.new,wts.new[,2],type='l',lty=3, xlim=c(0,0.02), main='UUP')
lines(muP.test,wts.test[,2],type='l',col='red')
plot(muP.new,wts.new[,3],type='l',lty=3, xlim=c(0,0.02), main='FXE')
lines(muP.test,wts.test[,3],type='l',col='red')
plot(muP.new,wts.new[,4],type='l',lty=3, xlim=c(0,0.02), main='FXY')
lines(muP.test,wts.test[,4],type='l',col='red')
plot(muP.new,wts.new[,5],type='l',lty=3, xlim=c(0,0.02), main='FXNAX')
lines(muP.test,wts.test[,5],type='l',col='red')
plot(muP.new,wts.new[,6],type='l',lty=3, xlim=c(0,0.02), main='SEGA.MI')
lines(muP.test,wts.test[,6],type='l',col='red')
```

Plot of SML, Efficiency Frontier, Global Portfolio, Tangency Portfolio and Risk-free Rate
```{r}
mean = apply(R,2,mean)
cov = cov(R)
amat = cbind(rep(1,6),mean,diag(1,nrow=6))
wts = matrix(0,nrow=500,ncol=6)
muP = seq(min(mean)+0.0001,max(mean)-0.0001,length=500)
sdP = muP  

for (i in 1:length(muP)){
  bvec=c(1,muP[i],rep(0,6))
  result = solve.QP(Dmat=2*cov, dvec=rep(0,6), Amat=amat,
                    bvec = bvec, meq=2)
  sdP[i] = sqrt(result$value)
  wts[i,] = result$solution
}
wts <- round(wts, 6)
colnames(wts) = c('QQQ','UUP','FXE','FXY','FXNAX','SEGA.MI')
tail(wts)

par(mfrow = c(1,1))
plot(sdP,muP,type="l",xlim=c(0,2.5),ylim=c(0,0.15),lty=3) 


# 3-months Treasury Rate as of 7 Nov 2021
rfr = 0.05/252
points(0,rfr,cex=1.5,pch="*",col="red")  
SR=(muP-rfr)/sdP
ind=(SR==max(SR)) 
options(digits=3)


# Print weights of the tangency portfolio
wts[ind,]
sdP[ind]
muP[ind]
lines(c(0,2.5),rfr+c(0,2.5)*(muP[ind]-rfr)/sdP[ind],
      lwd=1.5,lty=1,col="blue")
points(sdP[ind],muP[ind],cex=1.5,pch="*",col="red")

# Show global minimum variance portfolio and plot efficient frontier
ind2 = (sdP == min(sdP))
points(sdP[ind2],muP[ind2],cex=1.5,pch="+") 
ind3 = (muP > muP[ind2])

lines(sdP[ind3],muP[ind3],type="l",xlim=c(0,0.25),
      ylim=c(0,.15),lwd=1.5,col="red")
ind4=!ind3
lines(sdP[ind4],muP[ind4],type="l",xlim=c(0,0.25),
      ylim=c(0,.15),lwd=1.5,col="green") 
text(0.42,rfr,"Risk free rate",cex=0.8)

# Annualised US CPI inflation rate as of May 2021 = 5%
cpi = 5/252
abline(h = cpi, col="orange")
text(1.5, cpi + 0.01, "daily inflation rate", srt=0.2, col="orange")
```



```{r}
#BENCHMARK RETURN SP500
getSymbols("^GSPC",from='2011-06-01',to='2021-05-31',auto.assign = TRUE)
BR=GSPC[,6]

df=read.csv('prices_NEW.csv')
date=as.Date(df$Date,format="%m/%d/%Y")

BR=diff(log(xts(BR)))
ret=diff(log(xts(df[,2:7],order.by=date)))
         
ret=cbind(ret,BR)
ret=na.omit(ret)

R.new = ret*100
BR=R.new[,7]
R.new=R.new[,1:6]

#MEASURE OF PERFORMANCE
rfr = 0.05/252
mar=0.015
wts=c(0.1266,0.1288,0,0,0.6708,0.0739)
sdP=0.209
muP=0.0216
muBR=mean(BR)
sdBR=sd(BR)

# calculate portfolio weighted return 
ret.P=R.new%*%wts

# sharpe ratio 
SR=(muP-rfr)/sdP
sr.sp=(muBR-rfr)/sdBR

# roy's safety first ratio
SFR=(muP-mar)/(sdP)
sfr.sp=(muBR-mar)/sdBR

# treynor's ratio
mmP.m=lm(ret.P~BR)
TR=(muP-rfr)/as.numeric(mmP.m$coefficients[2])
  
# sortino ratio
DD=ifelse(ret.P<mar,1,0) 
DD.port=subset(ret.P,DD==1)
DDSD=sd(DD.port)
STR=(muP-mar)/DDSD

DD2=ifelse(BR<mar,1,0) 
DD2.port=subset(BR,DD2==1)
DDSD2=sd(DD2.port)
STR.SP=(muBR-mar)/DDSD2

# information ratio
IR=mean(ret.P-BR)/sd(ret.P-BR)

# print
cat(" Sharpe Ratio = ",SR,"\n","Safety First Ratio = ",SFR,"\n","Treynor Ratio = ",TR,"\n","Sortino Ratio =",
    STR,"\n","Information Ratio =",IR)


cat(" Benchmark Sharpe Ratio = ",sr.sp,"\n","Benchmark Safety First Ratio = ",sfr.sp,"\n","Benchmark Sortino Ratio =",
    STR.SP,"\n")